Color- and piece-blind chess

### 2019-03-16 chess/papers/blind.tex
Multi-round elo, quartiles, generate heatmap png for figure. Submitted versions of papers

It is easy to beat this chess engine, by tricking it as in
Figure~\ref{fig:trick}, although this involves unnatural moves, so it
may only apply if you know how it works.
% XXX example game?
Measuring how well it plays in an absolute sense is a subject of some
interest, so I wrote a separate paper about that~\cite{eloworld}. This
algorithm, called \verb+blind_yolo+, had an Elo World score of XXX. It
beats a purely random player with a score of 101 wins, 27 losses, and
389 draws. Making moves purely at random is one of the few fair
comparisons, since the random strategy also works with color- and
piece-blind chess.

@@

This version, called \verb+blind_kings+, performs consistently better
than \verb+blind_yolo+ (63 wins, 45 losses, 412 draws).
% XXX could run a lot more games between these two.
% as white: 31/24/207, as black 21/32/205
It had an Elo World score of XXX.

@@

(XXX evaluation here)

>>>>

It is easy to beat this chess engine, by tricking it as in
Figure~\ref{fig:trick}, although this involves unnatural moves, so it
may only apply if you know how it works.
% XXX example game?
Measuring how well it plays in an absolute sense is a subject of some
interest, so I wrote a separate paper about that~\cite{eloworld}. This
algorithm, called \verb+blind_yolo+, had an Elo World score of $489 \pm 2$. It
beats a purely random player with a score of 101 wins, 27 losses, and
389 draws. Making moves purely at random is one of the few fair
comparisons, since the random strategy also works with color- and
piece-blind chess.

@@

This version, called \verb+blind_kings+, performs a small amount better
than \verb+blind_yolo+ (63 wins, 45 losses, 412 draws).
% XXX could run a lot more games between these two.
% as white: 31/24/207, as black 21/32/205
It had an Elo World score of $502 \pm 3$.

@@

This version, \verb+blind_spycheck+, works significantly better than
\verb+blind_kings+. It has an Elo World score of $547 \pm 1$, somewhere
between a 93.75--96.875\% dilution of \verb+stockfish1m+ (the third
best non-engine player).
